Giant Low Surface Brightness Galaxies As Merger Remnants

### 2015-10-07 glsb.tex
minor updates

Points to cover in intro
\begin{itemize}
\item{GLSB galaxies are really big spirals}
\item{Typically classified as extreme spirals obsessionally}
\item{but HST observations of Malin~1 show it is a regular galaxy with a distinct extended disk \citet{Barth07}}
\item{Models for GLSB formation}
  \begin{itemize}
  \item{regular growth (maybe like polar ring galaxies, or just the large end of spirals)}
  \item{faded collisional ring. \citet{Mapelli08, Mapelli12} }
  \item{high angular momentum accretion event. \citet{Pen06}}
  \end{itemize}
  \item{Discuss how, if GLSBs are merger remnants, they represent a unique possibility to trace the dark matter halo of elliptical galaxies.  }
\end{itemize}

@@

\citet{Kasparova14} has an amazing analysis of Malin 2.  They combine ARC photometry, DIS spectra, and Gemini spectra to mass-model the system.  They find the broadband colors are not consistent with a catastrophic formation, but are best fit by exponentially declining SFH.  They think the main difference between Malin~2 and non-giant LSB galaxies is the dark matter halo scale.  I think this is begging the question a little bit

@@

Both of our objects have been observed with SDSS, making it possible to compare them to a large number of systems.  The outer disks of GLSBs are faint enough that the SDSS photometric pipeline effectively ignores them.

@@

Papers that have large \HI\ rotation curves that I might compare to:
\citet{DeBlok2008,Swaters09,Verheijen01}

@@

%/astro/store/shared-scratch1/yoachim/Research/GLSB/THINGS/thingsplot.py
\begin{figure}
\epsscale{.5}
\plotone{Plots/things.eps}
\epsscale{1}
\caption{ Comparison of the GLSB disks with other galaxy disks from the literature.  THINGS data taken from \citet{DeBlok2008}, Malin 1 from \citet{Moore06}, Malin 2 and UGC 6614 from \citet{Pickering97}.  Here, $R_{max}$ is the maximum radius with an \HI\ detection for the THINGS galaxies and the maximum radius with a stellar flux detection for Malin~1.  It is interesting to note that the \emph{stellar} disks of GLSB galaxies can be larger than the \HI\ disks of nearby systems.  \label{disk_comp}}
\end{figure}

@@

\appendix
\section{SDSS SQL quarries} \label{SQL}
To build our sample of comparison galaxies from SDSS, we used the CasJobs interface to query the SDSS DR10 database.

>>>>

@@

XXX-\citet{Kasparova14} has an amazing analysis of Malin 2.  They combine ARC photometry, DIS spectra, and Gemini spectra to mass-model the system.  They find the broadband colors are not consistent with a catastrophic formation, but are best fit by exponentially declining SFH.  They think the main difference between Malin~2 and non-giant LSB galaxies is the dark matter halo scale.  I think this is begging the question a little bit

@@

Both of our objects, as well as Malin 1, have been observed with SDSS, making it possible to compare them to a large number of systems.  The outer disks of GLSBs are faint enough that the SDSS photometric pipeline effectively ignores them.

@@

%Papers that have large \HI\ rotation curves that I might compare to:
%\citet{DeBlok2008,Swaters09,Verheijen01}

@@

%/astro/store/shared-scratch1/yoachim/Research/GLSB/THINGS/thingsplot.py
\begin{figure}
\epsscale{.5}
\plotone{Plots/things.eps}
\epsscale{1}
\caption{ Comparison of the GLSB disks with other galaxy disks from the literature.  THINGS data taken from \citet{DeBlok2008}, Malin 1 from \citet{Moore06}, Malin 2 and UGC 6614 from \citet{Pickering97}.  Here, $R_{max}$ is the maximum radius with an \HI\ detection for the THINGS galaxies, Malin~2, and UGC~6614 and the maximum radius with a stellar flux detection for Malin~1.  It is interesting to note that the \emph{stellar} disks of GLSB galaxies can be larger than the \HI\ disks of nearby systems.  \label{disk_comp}}
\end{figure}

@@

\appendix
\section{SDSS SQL Querries} \label{SQL}
To build our sample of comparison galaxies from SDSS, we used the CasJobs interface to query the SDSS DR10 database.
